\begingroup

\phantomsection % Ensures the PDF bookmark points to the exact top of the page
\addcontentsline{toc}{chapter}{ABSTRACT} % Adds 'ABSTRACT' to the ToC
\begin{center}
	\fontsize{14bp}{1.5\baselineskip}\selectfont \textbf{ABSTRACT}
\end{center}
\vspace{1.5\baselineskip} % Exact 1.5 line spacing gap

% 3. The tabular info section
\noindent
\begin{tabular}{@{}p{3.5cm} @{}c@{ } p{10.5cm}@{}}
	Full Name      & : & \AUTHOR \\[8pt]
	Study Program  & : & \STUDYPROGRAM \\[8pt]
	Title          & : & \TITLE \\[8pt]
	Supervisor     & : & \SUPERVISORONE 
\end{tabular}

\skiplines{1.5}

\noindent The management of Computer-Aided Design (CAD) assets is currently hindered by a reliance on manual annotation and the limitations of existing automated classification methods. Current approaches often require lossy conversion to visual representations or depend on synthetic construction histories unavailable in industrial Boundary Representation (B-Rep) files. This study proposes a novel Transformer-based architecture for the direct classification and annotation of raw STEP files.
Central to this methodology is a Hierarchical Dual-Stream Tokenizer designed to process irregular/non-standardized topological structure of B-Rep graphs. The pipeline implements Semantic Macro-Compression to reduce graph complexity and utilizes Canonical Normalization via Principal Component Analysis (PCA) to ensure translational and rotational invariance. To resolve graph isomorphism ambiguity, the system applies a deterministic Topological Linearization using a hierarchical sorting key. The resulting model utilizes a Dual-Stream Encoding strategy, fusing discrete semantic tokens with complex-valued geometric embeddings through a Geometry-Infused Attention mechanism and Rotary Positional Embeddings (RoPE). Validated against a hybrid dataset constructed from Text2CAD, ABC, and TraceParts using a Human-in-the-Loop pipeline, this approach effectively captures high-level functional identity without reconstructing procedural history.

\skiplines{1}

\noindent \textbf{Keywords:} CAD, tokenizer, STEP, B-rep, NURBS, compression, vector embeddings, inter-rater reliability
\endgroup
\pagebreak